\chapter*{Acknowledgement}
We would first like to thank our supervisor, Heri Ramampiaro, for allowing us to work on the project. His guidance, support, and encouraging feedback have been invaluable. He also gave us many chances to showcase and discuss our work, which we found both inspiring and educational.

We would also like to thank our co-supervisors, Associate Professor Espen Alexander F. Ihlen and PhD Candidate Felix Tempel. The guidance meetings have been instrumental in our project's success, alongside their expert advice and continuous support. We are deeply grateful for their invaluable contribution to our learning experience.

Lastly, we want to thank our friends. Your friendship, helpful advice, and all the fun times we have had together truly helped us through our time at NTNU. We are so grateful for your support during this part of our lives. We also want to express our gratitude to our families for all your support and motivating words. 

\begin{flushright}
\textit{To Zaim: I want to thank you for all our memories; it's been a blast! Thank you for being a fellow student, colleague, collaborator, problem-solver, and, most importantly, a best friend through my five years at NTNU.} \\
- Max
\end{flushright}

\begin{flushright}
\textit{Max, the past five years have been an incredible journey filled with both friendship and partnership. Our shared experiences, from late-night study sessions to exhilarating concerts, have only served to deepen and strengthen our bond. Your support and friendship have been invaluable; I am deeply grateful. Thank you.} \\
- Zaim
\end{flushright}


