\chapter*{Acknowledgement}
We would first like to thank our supervisor, Heri Ramampiaro, for allowing us to work on the project. His guidance, support, and encouraging feedback have been invaluable. He also gave us many chances to showcase and discuss our work, which we found both inspiring and educational.

We would also like to thank our co-supervisors, Associate Professor Espen Alexander F. Ihlen and PhD Candidate Felix Tempel. Their expert advice and continuous support have been instrumental in our project's success. In addition, they provided us with constructive critiques and guidance that significantly improved our work. We are deeply grateful for their invaluable contribution to our learning experience.

Lastly, we want to thank our friends. Your friendship, helpful advice, and all the fun times we have had together truly helped us through our time at NTNU. We are so grateful for your support during this part of our lives.

\begin{flushright}
\textit{To Zaim: Thank you for being a fellow student, colleague, collaborator, problem-solver, and, most importantly, a best friend through my five years at NTNU.} \\
- Max
\end{flushright}

\begin{flushright}
\textit{To Max: The past five years have been an incredible journey of friendship and partnership. Our shared experiences, from late-night study sessions to exhilarating concerts, from challenging school projects to roaring cheers on the football field, our bond has grown deeper and stronger with every shared experience. Your support and friendship have been invaluable; I am deeply grateful. Thank you, my friend, for being a part of my life, and I look forward to the adventures yet to come.} \\
- Zaim
\end{flushright}


