\chapter{Method}\label{method}
Chapter 4 will discuss the different methods utilised in the experiments and a rationale behind the methods. The chapter begins with an overview of the planned research plan and explains how the benchmark is developed. After that, various zero-cost proxies, such as \gls{FLOPs}, Params, EPE-NAS, L2-norm, Plain, Zen-score, and GradSign, are mathematically explained. Also, the implementation of the zero-cost proxies is provided. The chapter then looks into the combination of zero-cost proxies, discussing how to use the weighted arithmetic mean to combine proxies to rank architectures. Finally, the chapter evaluates the effectiveness of the different methods and techniques used in the study.

\section{Research Plan}
In this section, the research methods employed in this study are presented. As \cref{fig:research_flowchart} illustrates, the process comprises several steps. First, the process starts with generating random architectures, followed by comprehensive training of these architectures for benchmarking purposes. Subsequently, a zero-cost proxy framework is established, and data regarding the performance of zero-cost proxies is collected. Lastly, a quantitative analysis is conducted using the acquired data to conclude the performance and effectiveness of the zero-cost proxies. 
\clearpage

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
  node distance=1cm,
  process/.style={rectangle, rounded corners, minimum width=4cm, minimum height=1.5cm, text width=3.6cm, align=center, draw=black},
  process1/.style={process, fill=gray!20},
  process2/.style={process, fill=gray!50},
  arrow/.style={thick,->,>=stealth, line width=1.5pt, draw=gray}
]

\node (step1) [process1] {Generate Random Architectures};
\node (step2) [process2, below=of step1] {Conduct Comprehensive Training on Architectures for Benchmarking};
\node (step3) [process1, below=of step2] {Establish Zero-Cost Proxy Framework};
\node (step4) [process2, below=of step3] {Collect Data on Zero-Cost Proxies Performance};
\node (step5) [process1, below=of step4] {Perform Quantitative Analysis Using Collected Data};
% Add more nodes for additional steps

\draw [arrow] (step1) -- (step2);
\draw [arrow] (step2) -- (step3);
\draw [arrow] (step3) -- (step4);
\draw [arrow] (step4) -- (step5);
% Add more arrows for additional steps

\end{tikzpicture}
\caption{Flowchart illustrating the research process.}
\label{fig:research_flowchart}
\end{figure}

\input{chapters/4-method/dataset.tex}
\input{chapters/4-method/benchmark.tex}
\input{chapters/4-method/ZC-Proxies.tex}
\input{chapters/4-method/zero_cost_framework}
\input{chapters/4-method/Correlation}
\input{chapters/4-method/warmup}
\input{chapters/4-method/combining_zero_cost_proxies}