\chapter{Results}\label{results}
\begin{comment}
In this chapter, we present the results of our investigation into the use of zero-cost proxies in neural architecture search (NAS) for graph convolutional networks (GCN). We address three research questions about using proxies in NAS for GCN, as outlined in the introduction chapter (\ref{section:goalsandrq}). Specifically, we analyze the effectiveness of different zero-cost proxies in ranking GCN architectures, examine the impact of incorporating proxies in the NAS algorithm and investigate the effectiveness of using an ensemble of proxies in NAS.
\end{comment}

\begin{comment}
Chapter 5 of the thesis presents the results of an investigation into the use of zero-cost proxies in neural architecture search for graph convolutional networks. The chapter includes a section on correlation and a vote section that analyze the effectiveness of different zero-cost proxies in ranking GCN architectures. Additionally, a section on supervised learning using Recursive Feature Elimination with Cross-Validation and Pointwise Ranking with Regression and Cross-Validation is included. Finally, the chapter addresses three research questions about the use of proxies in NAS for GCN and examines the impact of incorporating proxies in the NAS algorithm and investigates the effectiveness of using an ensemble of proxies in NAS.
\end{comment}

This chapter outlines the study's findings, responding to the defined research questions. Next, the 'Correlation Analysis' section evaluates the capability of zero-cost proxies in ranking GCN architectures concerning their validation accuracy. Subsequently, the analysis of correlation during the warm-up phase of GCN training is identified. Lastly, the 'Vote' and 'Weighted Arithmetic Mean' section examines techniques for combining zero-cost proxies to improve efficiency and accuracy in NAS algorithms.


\input{chapters/5-results/correlation}
\input{chapters/5-results/vote}
\input{chapters/5-results/warmup}
\input{chapters/5-results/Weighted Average}



%\input{chapters/5-results/supervised_learning}

