\chapter{Discussion}\label{discussion}
\begin{comment}
This chapter aims to analyse and interpret the findings of our study in the context of the overall goal and research questions. Our research aimed to improve and optimise the efficiency of neural architecture search (NAS) with graph convolutional networks (GCN) for human action recognition (HAR). The authors will first interpret the results of each research question and discuss their implications in the context of the overall goal. We will then consider the significance of our findings and their potential impact on the field of NAS with GCN for HAR. Furthermore, we will acknowledge the limitations of our study. 
\end{comment}
Chapter 6 of the thesis discusses the study's findings on improving and optimising the efficiency of NAS with GCN for HAR. The chapter aims to analyse and interpret the results of each research question and their implications in the context of the overall goal. The authors also discuss the significance and potential impact of the findings on the field of NAS with GCN for HAR and acknowledge the study's limitations. In addition, a discussion on the overall environmental implication is included. 

\begin{comment}
    In this chapter, the method and experimental result are analysed and discussed regarding
their merits and limitations in light of research from the literature. The chapter is
concluded with a discussion of how the research questions are answered.
\end{comment}
\input{chapters/6-discussion/Interpretation}
%\input{chapters/6-discussion/Significance}
\input{chapters/6-discussion/Limitations}
\input{chapters/6-discussion/Environment}
