 \section{Background and Motivation}
This thesis is written as part of a project named DeepInMotion. Researchers from the \Gls{NTNU} and St. Olavs Hospital cooperate in a cross-disciplinary collaboration involving child physiotherapists, paediatricians, neonatologists, movement scientists and computer engineers. The project has developed a pipeline for detecting \Gls{CP} in infants by providing a video of the infant's movement. The pipeline employs a \Gls{CNN} to accurately extract movement from 2D images or videos \autocite{groos2021efficientpose}. A \gls{GCN} then processes the output to predict \gls{CP} in high-risk infants at three months of age \autocite{groos2022convolutional}. 

The \gls{CP}-prediction pipeline used \gls{NAS} to automatically find a suitable architecture which yields good results in regards to the performance of the model. However, the search could be faster and more efficient while providing good results. Performance predictor is a way of estimating the relative performance of an architecture for a given problem and can be far more effective than training the architecture until convergent. There needs to be more research on using zero-cost proxies with \gls{GCN}. This gap in the literature means that potential improvements in the efficiency and performance of \gls{NAS} when using \gls{GCN} might still need to be discovered. The \gls{CP}-prediction pipeline could be enhanced by addressing this gap, and additional knowledge about how zero-cost proxies can be used with graph-based learning could be gained. This research aims to explore the effectiveness of zero-cost proxies in conjunction with \gls{GCN} and uncover how they perform. 