\section{Contributions}

This thesis presents several critical contributions to the NAS field with GCNs for HAR. The following are the primary contributions made by this study:

\textbf{Investigation of Zero-Cost Proxies:} In this thesis, a thorough analysis of the relationship between zero-cost proxies and the performance of GCN models in HAR tasks is conducted. The study sheds light on the usefulness of using zero-cost proxies to estimate the performance of GCN architectures without the need for costly training. To our knowledge, this research represents the first in the literature to specifically explore the application of zero-cost proxies within the context of GCN tasks.

\textbf{Combining Zero-Cost Proxies:} The thesis presents effective methods, such as the majority vote method and the weighted arithmetic mean method, for combining different zero-cost proxies to improve the efficiency and accuracy of the NAS process. 

\textbf{Environmental Considerations:} The study highlights the importance of considering the environmental implications of NAS and artificial intelligence research. Furthermore, the study contributes to developing more sustainable practices in the field by reducing the NAS process's computational demands and training time.

\begin{comment}
    
\textbf{Identification of Limitations and Future Research Directions:} The thesis acknowledges the current study's limitations and provides a roadmap for future research to address these limitations.
\end{comment}

These contributions advance the understanding of NAS with GCNs in the context of HAR and provide a foundation for further exploration of zero-cost proxies and their potential applications.